Language-Parametric Techniques for Live Probes

### 2023-08-01 paper/paper.tex
Clean and add sloc

\begin{table}[!ht]
  \centering
  \begin{tabular}{|l|l|l|}
  \hline
      \textbf{} & SLOC Live Probe Server & SLOC KAA \\ \hline
      \textbf{Java JDI} & 592 (Java) & 15 (Java) \\ \hline
      \textbf{DAP Base} & 267 (Python) & ~ \\ \hline
      \textbf{DAP Java} & 352 (Python) & 91 (Java) \\ \hline
      \textbf{DAP Python} & 142 (Python) & 26(Python) \\ \hline
      \textbf{DAP Javascript} & 257 (Python) & 24(Javascript) \\ \hline
      \textbf{DAP C} & 188 (Python) & 14(C) \\ \hline
  \end{tabular}
  \caption{SLOC of the Live Probe Server and Keep Alive Agent (To update after new Java changes)}
  \label{tab:sloc}
\end{table}

@@

>>>>

@@

\subsection{Implementation specifications}

\begin{table}[!ht]
  \centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabularx}{0.7\linewidth}{lc*{4}{>{\RaggedRight\arraybackslash}X}}
      \toprule
      Implementation & SLOC Live Probe Server & SLOC KAA \\
      \midrule
      Java JDI & 527 (Java) & 77 (Java) \\ 
      DAP Base & 267 (Python) & ~ \\ 
      DAP Python & 142 (Python) & 26(Python) \\ 
      DAP Java & 352 (Python) & 115 (Java) \\ 
      DAP Javascript & 257 (Python) & 24(Javascript) \\ 
      DAP C & 188 (Python) & 14(C) \\
      \bottomrule
  \end{tabularx}
  \caption{SLOC of the Live Probe Server and Keep Alive Agent}
  \label{tab:sloc}
\end{table}

The table \ref{tab:sloc} shows the number of lines of code for the server part and the KAA for each implementation, with the language in brackets. The DAP Base line corresponds to the common code used by the other DAP-based implementations.
The tests were carried out with OpenJDK 20.0.2 for Java, Python 3.11.2 for Python and Node 18.16.1 for Javascript. The C code was compiled using GCC 13.1.1. The machine used to carry out the evaluations has an AMD Ryzen 5 2500U CPU and 8Gb of RAM.
